Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-07 windheat.tex
Fixing citations at the end of appendix.

We show $V_{\rm W}$ for different star formation histories in
Fig. \ref{NickPlot2}.  In particular, we use Eqs. 17-20 from Moster et
al and the $M_{\rm BH}-M_{\rm halo}$ relation from Bandara et al {\bf
(NCS: add real refs)} to define $S(t)$ for particular galaxies.  It
seems that ``bumpy'' SF histories severely diminish $V_{\rm w}$ if the
timescale for SF variability is a factor of a few or more greater than
the duration of high-velocity winds (either 10 or 40 Myr).

>>>>

We show $V_{\rm W}$ for different star formation histories in
Fig. \ref{NickPlot2} {\bf AG: this plot still uses the old ad hoc vw
  prescription? If so it would need to be fixed. In any case, we still
  differ in detail on the vw from stars}.  In particular, we use
Eqs. 17-20 from \citet{MosterNaab+:2013a} and the $M_{\rm BH}-M_{\rm
  halo}$ relation from \citet{BandaraCrampton+:2009a} to define $S(t)$
for particular galaxies.  It seems that ``bumpy'' SF histories
severely diminish $V_{\rm w}$ if the timescale for SF variability is a
factor of a few or more greater than the duration of high-velocity
winds (either 10 or 40 Myr).
